% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\usepackage{hyperref}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
    {\LARGE \textbf{John Litborn}}

    john.litborn@pm.me
    \ \textbullet \ \
    Linköping, Sweden
\end{center}

\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Education group for Programming and Programming
        Didactics}}
        {\textbf{Linköping University}}
    \\
    \textbf{Department of Computer and Information Science}
    \\
    \headerrow
        {\emph{Amanuensis, Course Assistant, Head Assistant}}
        {\emph{2013 -- 2017}}
    \begin{itemize*}
        \item Recruited my second year at university, I taught courses in Python,
            \CPP, Ada and Matlab.
        \item Primarily introductory courses, where I held lessons with repetition
            and shared problem solving, lab assistant where I answered questions and
            helped solve problems, and correcting lab hand-ins and exams.
        \item Later on I also held more advanced courses, teaching the \CPP  standard
            library, git, object-oriented programming or unit-testing.
            I was also advisor on projects and grading documentation
            and hand-ins, and as head assistant taking on light
            administrative and managerial duties for students and other
            assistants.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Division for Artificial Intelligence \& Integrated Computer Systems}}
        {\textbf{Linköping University}}
    \\
    \textbf{Department of Computer and Information Science}
    \\
    \headerrow
        {\emph{Course Developer, Software Developer}}
        {\emph{Summer of 2014 \& 2015}}
    \headerrow
        {\url{https://github.com/h00701350103/XPilot-AI\_LiU\_fork}}
        {Python, C, HTML}
    \begin{itemize*}
        \item After being unhappy with a course and it's software and
            giving feedback to the professor, I was offered a summer job
            to improve it. Where I remade the assignments and improved the
            Python API for XPilot, a 2D multiplayer space shooter, that was
            used in the course.
        \item I overhauled the structure of the assignments, changed,
            removed and added several ones and wrote better and clearer
            instructions and documentation.
        \item The XPilot-AI API in use was developed at Connecticut College,
            and after discussions with them I forked the project and begun
            modifying the C-Python interface to fix bugs and add features to
            suit our needs.
        \item My second year working on it I also started modifying the
            client-server netcode to send more data so the
            client-side API for example didn't have to re-calculate the speed
            of objects.
    \end{itemize*}

    \item
    \headerrow
            {\textbf{Ericsson, HiQ}}
            {\textbf{Linköping}}
    \\
    \headerrow
            {\emph{IT-Consultant}}
            {\emph{Mar -- Oct 2017}}
    \begin{itemize*}
        \item Hired by the consulting firm HiQ to work at Ericssons main
            offices in Linköping in a team with other consultants.
        \item Our task was to updated 4G base-station unit tests written in
            Erlang to work in a virtualized environment. I was the git-master
            in the team, and helped the other team members when they
            encountered problems with Git or Linux.
        \item I was also responsible for updating our sections on the
            internal Wiki, and wrote python and bash scripts for myself and
            other team members to simplify rote tasks.
    \end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Linköping University, Faculty of Science and Engineering}}
        {\emph{2012 -- 2014, 2020 -- 2021}}
    \\
    \headerrow
        {\emph{Computer Engineering}}
        {\emph{120 Credits}}
    \begin{itemize*}
        \item I have almost exclusively studied part-time, early on
            because of parallel work at the university, later on because of
            mental health issues.
        \item \( 2/3 \) of credits are in programming in a diverse set of
            languages (Python, \CPP, C, Java, Ada, VHDL, Prolog, Assembly, GNU
            MathProg), with a focus on algorithm construction, optimization and
            low-level code. \( 1/3 \) of credits are in math courses.
        \item My second year I won a programming competition in a course on
            Computer Hardware and Architecture,
            which consisted of writing a sorting algorithm in microcode for
            a low-level simulated computer. My solution also beat the
            professors best implementation, and outclassed the previous student
            record.
    \end{itemize*}

\end{itemize}


\hrule
\vspace{-0.4em}
\subsection*{Core Technical Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
    \item[Languages:]
        Python, \CPP, C, Ada
    \item[Tools:]
        Arch Linux, NeoVim, git, command line tools (gdb, pdb, mypy, linters)
\end{description*}
\end{indentsection}


% \hrule
% \vspace{-0.4em}
\subsection*{Personal Projects}

\begin{itemize}
    \parskip=0.1em

    \item
    \headerrow
        {\textbf{Necro Score Bot}}
        {\emph{2015-present}}
    \\
    \headerrow
        {\url{https://github.com/h00701350103/necro\_score\_bot}}
        {Python, 1500 lines of code}
    \begin{itemize*}
        \item Lacking a good way to track scores on the leaderboards in the
            indie rhythm roguelike Crypt of the Necrodancer I decided to write
            a twitter bot that pulls leaderboards from the Steam API, parses
            them, and tweets out notable updates.
        \item Players can add a link to their twitter in their steam profile,
            which lets the bot tag them and post less notable updates only
            to them and their followers. It auto-detects cheated or bugged
            scores and notifies the developers. It supports 16 different
            characters, 4 run types, and all permutations of 9 game modes for a
            total of over 400 leaderboards.
        \item Uses the twitter API, queries both the official and legacy steam
            API as well as raw html requests. Discord support and both
            speedrunslive and NecroLab (a community power-ranking site)
            leaderboard support was implemented but never activated. Also
            interfaces with toofz, another community site.
        \item Parses XML, json \& pickle. Multithreaded, thorough error
            handling, config file and command line flags and modularly written
            with >120 functions across 10 files.
        \item Initial development spurt during 2015, and a second spurt in 2017
            to make it work with the DLC. Has multiple small pull request from
            other community members and is kept running and maintained to this
            day by them.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Seat Exchange Bot}}
        {\emph{May-June 2019}}
    \\
    \headerrow
        {\url{https://github.com/h00701350103/seat\_exchange}}
        {Python, 3500 lines of code}
    \begin{itemize*}
        \item One of several "small" discord bots I've whipped up. This one
            during a bout of interest in the Korean game show The Genius, where
            I adapted and implemented one of the games from the show.
        \item The bot supports 40 different commands, different player counts,
            computer players, multiple simultaneous games and permissions.
        \item The code is object-oriented, easily extendable, statically
            typed (using mypy), fully adheres to PEP8 and official python
            coding standards (passes pylint with very few disabled checks) and
            even has some comments.
    \end{itemize*}

    \item
    \headerrow
        {\textbf{Home Automation}}
        {\emph{2016-present}}
    \\
    \headerrow
        {}
        {>400 actions across >30 actions}
    \begin{itemize*}
        \item Using the Android scripting application Tasker I've created a
            system for managing my life, notifying when to wake up, take
            medication \& vitamins, eat, sleep and other reminders. Logs
            everything to the calendar, as well as time-to-fall-asleep and
            sleep duration, enabling statistics.
            Also assists with daily diary taking and evaluating drugs with
            self-blinded experiments.
        \item Interfaces with my smartwatch, a Pebble Time, and widgets
            custom-created with KWGT. Planning to interface it to my self-built
            automatic roller blinds running on an Arduino.
    \end{itemize*}

\end{itemize}

\end{document}
